\section{Stochastic Boolean satisfiability}
\label{sect:related-work-ssat}

SSAT~\cite{Littman2001,SATHandbook-SSAT} is first formulated by Papadimitriou
and interpreted as \textit{games against nature}~\cite{Papadimitriou1985}.
It lies in the same PSPACE-complete~\cite{Stockmeyer1973} complexity class as QBF.

Exploiting randomized quantifiers,
SSAT is capable of modeling a variety of computational problems inherent with uncertainty~\cite{Hnich2011},
such as probabilistic planning~\cite{Kushmerick1995,Littman1998},
Bayesian-network inference~\cite{Cooper1990,Jensen1996,Dechter1998,Bacchus2003},
and trust management~\cite{SATHandbook-SSAT}.
Recently, the quantitative information-flow analysis for software security is also formulated
as E-MAJSAT~\cite{Fremont2017},
and bi-directional polynomial-time reductions between SSAT and POMDP are established~\cite{Salmon2020}.

A number of SSAT solvers have been developed.
Among the prior efforts made to approach SSAT,
most of them are based on Davis-Putnam-Logemann-Loveland (DPLL) search~\cite{Davis1962}.
For example,
solver \maxplan~\cite{Majercik1998} encodes a conformant planning problem as an E-MAJSAT formula
and improves the solving efficiency by pure variables, unit propagation, and subproblem memorization;
solver \zander~\cite{Majercik2003} deals with partially observable probabilistic planning by formulating the problem as a general SSAT formula and incorporates several threshold-pruning heuristics to reduce the search space.
Solver \dcssat~\cite{Majercik2005} divides an SSAT formula into several smaller SSAT formulas and conquers them with a DPLL-based algorithm.
The solutions to the separate SSAT problems are then combined into an optimal solution to the entire formula.
The formula splitting is tailored to exploit the structural characteristics of probabilistic planning problems,
which often contain similar clauses to encode the state-transition mechanism across different stages.
The divide-and-conquer approach of \dcssat achieves several orders of magnitude speedup than its predecessor \zander.
Approximate solving~\cite{Majercik2007} and resolution rules~\cite{Teige2010} for SSAT have also been addressed.
Techniques from \textit{knowledge compilation} have also been exploited to solve E-MAJSAT formulas.
Solver \complan~\cite{Huang2006} compiles the matrix of an E-MAJSAT formula into its
\textit{deterministic, decomposable negation normal form} (d-DNNF)~\cite{Darwiche2001,Darwiche2002dDNNF},
and performs a branch-and-bound search.
It is further improved by an enhanced bound computation method~\cite{Pipatsrisawat2009}.