First of all, I want to thank my advisor Prof. Jie-Hong Roland Jiang for guiding me through the journey in pursuit of a Ph.D. degree.
Roland's passion for research has pushed me to the best that I can achieve.
He dedicated much of his time to our collaboration, and many good ideas followed from our discussions.
I also want to thank my oral-defense committee members,
Prof. Dirk Beyer, Prof. Ichiro Hasuo, Dr. Victor N. Kravets, and Dr. Bow-Yaw Wang
for reviewing this dissertation and giving me much feedback during the oral defense.

A big thank you goes to all of my coauthors.
I have learned a lot from our collaboration and enjoyed working with you.
Especially, I want to thank Yen-Shi, with whom I developed much of the work in this dissertation.
I also want to thank my fellow students at ALCom-Lab.
The time we spent together in the lab was a lifetime memory and supported me at some difficult moments during my study.

Furthermore, I want to thank Victor, Ichiro, and Dirk for giving me opportunities to work at their institutes.
The experience of working in a different research group made my Ph.D. study more colorful and memorable.
I also want to thank the colleagues at IBM, the ERATO MMSD project, and SoSy-Lab
for helping me adapt to a new environment and enjoy the research and life abroad.
Particularly, I want to thank Chau-Chin for working and having fun together at IBM.
My first working experience abroad would not have been so comfortable without his company.
I want to thank Paolo and Shaukat for leading me into a new research field when I started at the ERATO MMSD project,
and J{\'e}r{\'e}my for all the unforgettable moments we spent together in OLDMAN.
I want to thank Martin for helping me find an apartment in Munich, and sharing an office with him is a great pleasure.
I am very grateful to Philipp, who helped me a lot during the pandemic lockdown.
Without his advice, my visit to Germany could not have been so fruitful and productive.
The concepts and skills I learned from him also helped me during the writing of the dissertation.

Finally, I want to thank my parents for their endless love and support.
I also want to say sorry to them because I might not always be together with them when they need me.