\chapter{Conclusion and Future Work}
\label{chap:conclusion-future-work}

In this dissertation,
we contributed to the research needs highlighted in~\cref{chap:introduction}.

The applicability of SSAT to the analysis of VLSI systems was examined.
We formulated a framework for the property evaluation of probabilistic design.
The average-case and worst-case analyses are encoded
as random-exist and exist-random quantified SSAT formulas, respectively.

Motivated by the emerging VLSI applications,
we further devised novel algorithms for random-exist and exist-random quantified SSAT formulas.
The proposed algorithms leverage the success from SAT/QBF-solving and model-counting communities
and advance the state-of-the-art of SSAT solving beyond the conventional DPLL-based search.
For random-exist quantified SSAT formulas,
we used minterm generalization and weighted model counting as subroutines
and employed SAT solvers and weighted model counters as plug-in engines.
For exist-random quantified SSAT formulas,
we proposed clause-containment learning,
which was inspired by clause selection from QBF solving.
Under the framework of clause-containment learning,
we explored three heuristics to strengthen learnt clauses.
Moreover, unlike previous exact approaches,
the proposed algorithms can solve approximate SSAT by deriving upper and lower bounds of satisfying probabilities.
Our evaluation showed the benefits of the proposed solvers over a wide range of formula instances.
Furthermore, our implementations and the benchmark suite of SSAT instances are open-source
for other researchers to base their work on top of our results.

To generalize SSAT beyond the PSPACE-complete complexity class for more complex problems,
we extended DQBF to its stochastic variant DSSAT and proved its NEXPTIME-completeness.
Compared to the PSPACE-complete SSAT,
DSSAT is more powerful to succinctly model NEXPTIME-complete decision problems with uncertainty.
We demonstrated the DSSAT formulation of the analysis to probabilistic/approximate partial design
and gave a polynomial-time reduction from the NEXPTIME-complete Dec-POMDP to DSSAT.

We highlight several directions for future investigation.
First, in order to improve the scalability of probabilistic property evaluation,
we are interested in approximate approaches based on simulation techniques.
In addition to the conventional Monte Carlo method,
circuit simulation based on symbolic sampling~\cite{KravetsDAC19ECOSampling} may have much potential.
Another line of on-going work is to develop solvers for arbitrarily quantified SSAT and DSSAT formulas.
Recently, clause selection has been adapted to solve random-exist quantified SSAT formulas
and combined with the clause-containment learning in a recursive manner to solve general SSAT~\cite{Chen2021}.
It is also extended to DQBF~\cite{Tentrup2019},
which might provide a promising framework for DSSAT solving.
From the view of practical implementation,
SSAT solvers will benefit from a tight integration with model-counting components.
More advanced data structures, e.g., d-DNNF~\cite{Darwiche2001,Darwiche2002dDNNF}, could be also integrated.
In particular, \textit{incremental} model counting might be a key step to boost the performance of SSAT solvers
if the computational efforts among different counting queries can be effectively shared.
Motivated by approximate model counting,
we also hope to pursue a similar formulation for SSAT solving.
Specifically, we envisage a unified SSAT framework that allows users to control the solution precision,
in order to trade inexactness for better scalability.
Finally, we would like to bring SSAT to different research fields, especially to machine-learning applications.
The SSAT solvers developed in this dissertation have been applied to verify the fairness of supervised-learning algorithms~\cite{Ghosh2021}.
According to the reported data~\cite{Ghosh2021},
using the proposed SSAT solvers achieves several orders of magnitude improvement over the state-of-the-art tools.
This success shows the great potential and benefit of SSAT solving.

\iffalse
    We have proposed a formal framework to probabilistic property
    evaluation, under the worst-case and average-case scenarios.
    Connections between probabilistic property evaluation and existing
    solving techniques have been established. A novel BDD-based SSAT solver is proposed. A comparative experimental study has been performed to assess the capabilities
    of different methods. Among the considered solutions, the proposed BDD-based SSAT solver, which makes use of circuit structures to construct BDD, currently tends to be the most robust in our experiments. Nevertheless, there are cases solvable only by approximate weighted model counting, but not by other methods. As the BDD-based method has its memory explosion problem, SSAT and model
    counting approaches based on CNF formula might be more viable than the BDD one if their efficiency would be improved in the future. Our results may benefit the synthesis of probabilistic design, perhaps not only for silicon but also for genetic circuits, which are intrinsically stochastic. For future investigation, Monte-Carlo simulation may be incorporated to our proposed formal methods.

    In this paper, we focused on solving random-exist quantified SSAT formulas.
    In contrast to the previous DPLL-based algorithms, we proposed a novel algorithm using SAT solver and weighted model counter as underlying engines to improve computational efficiency.
    Leveraging the great success of modern SAT solving techniques, the proposed algorithm outperforms the state-of-the-art method in the experiment on random $k$-CNF and strategic companies formulas.
    Moreover, unlike previous exact SSAT methods, the proposed algorithm can be easily modified to solve approximate SSAT by deriving upper and lower bounds of satisfying probability.
    We demonstrated the applicability of our SSAT solver to VLSI circuit analysis.
    While the state-of-the-art solver fails to compute the exact satisfying probability, the proposed method succeeded in finding bounds of the formulas.
    In several cases, the derived bounds are very close to, or even match the exact satisfying probability.
    This approximation flexibility of our method can be helpful when SSAT is applied to real-world applications.
    %This work might shed light on the application of solving approximate SSAT to real-world problems.
    For future work, we intend to extend the proposed algorithm to arbitrary quantified SSAT formulas.

    We developed a new approach to solving E-MAJSAT formulas. In contrast to prior methods based on DPLL search or knowledge compilation, we proposed the clause containment learning technique, inspired by clause selection recently developed in QBF evaluation, and design a novel algorithm to solve E-MAJSAT efficiently. Under the framework of clause containment learning, three enhancement techniques were proposed to improve the computational efficiency.
    Experiment results show the benefit of our method.
    %that our method achieves significant performance gains and memory savings over prior SSAT methods, and also provides useful lower bound information for cases where no information can be given by prior methods.
    For future work, we intend to solve SSAT with general prefix structure.

    In this paper, we extended DQBF to its stochastic variant DSSAT and proved its NEXPTIME-completeness.
    Compared to the PSPACE-complete SSAT, DSSAT is more powerful to succinctly model NEXPTIME-complete decision problems with uncertainty.
    The new formalism can be useful in applications such as artificial intelligence and system design.
    Specifically, we demonstrated the DSSAT formulation of the analysis to probabilistic/approximate partial design, and gave a polynomial-time reduction from the NEXPTIME-complete Dec-POMDP to DSSAT.
    We envisage the potential broad applications of DSSAT and plan solver development for future work.
    %\textcolor{blue}{
    We note that recent developments of \textit{clausal abstraction} for QBF~\cite{JanotaM15,RabeT15} and DQBF~\cite{Tentrup19} might provide a promising framework for DSSAT solving.
    Clausal abstraction has been lifted to SSAT~\cite{ChenHJ21}, and we are investigating its feasibility for DSSAT.
    %}
\fi